A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-11-25 kobakian-cook.Rmd
abstract rtweaks

---
title: A Hexagon Tile Map Algorithm for Displaying Spatial Data
author:
  # see ?rjournal_article for more information
  - name: Stephanie Kobakian
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    email:  stephanie.kobakian@monash.edu 
  - name: Dianne Cook
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    email:  dicook@monash.edu 
  - name: Earl Duncan
    affiliation: Queensland University of Technology
    address:
    - School of Mathematical Sciences
    email:  earl.duncan@qut.edu.au
abstract: >
  Spatial distributions have been presented on alternative representations of geography for many years. In modern times, interactivity and animation have allowed alternative displays to play a larger role. Alternative representations have been popularised by online news sites, and digital atlases with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results. The algorithm presented creates a display that uses tessellated hexagons to represent a set of spatial polygons. It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units, in light of their positions to points of interest. The display showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps. 
preamble: |
  % Any extra LaTeX you need in the preamble
bibliography: kobakian-cook.bib
output: rticles::rjournal_article
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: A Hexagon Tile Map Algorithm for Displaying Spatial Data
author:
  # see ?rjournal_article for more information
  - name: Stephanie Kobakian
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    email:  stephanie.kobakian@monash.edu 
  - name: Dianne Cook
    affiliation: Monash University
    address:
    - Department of Econometrics and Business Statistics
    email:  dicook@monash.edu 
  - name: Earl Duncan
    affiliation: Queensland University of Technology
    address:
    - School of Mathematical Sciences
    email:  earl.duncan@qut.edu.au
abstract: >
  Spatial distributions have been presented on alternative representations of geography, such as cartograms, for many years. In modern times, interactivity and animation have allowed alternative displays to play a larger role. Alternative representations have been popularised by online news sites, and digital atlases with a focus on public consumption. Applications are increasingly widespread, especially in the areas of disease mapping, and election results. The algorithm presented creates a display that uses tessellated hexagons to represent a set of spatial polygons, and is implemented in the R package called sugarbag. It allocates these hexagon in a manner that preserves the spatial relationship of the geographic units, in light of their positions to points of interest. The display showcases spatial distributions, by emphasising the small geographical regions that are often difficult to locate on geographic maps. 
preamble: |
  % Any extra LaTeX you need in the preamble
bibliography: kobakian-cook.bib
output: rticles::rjournal_article
editor_options: 
  chunk_output_type: console
---
